% About graphical library benchmark
The graphical library benchmark was performed in the same conditions for each library,
the idea was to test the Frames Per Second (FPS) to compare their performance.
Each program has a similar code structure, with the following conditions:
\begin{itemize}
	\item One thread in charge of feeding the plot with random data.
	\item A main thread to execute the program.
	\item A program widget without details, only the dynamic plotted data (axis, labels, etc)
\end{itemize}
The next step is a comparison between graphical libraries and study
the behavior with different latency times (data actualization rate), and finally
extract a conclusion about the best performing graphical library.
Finally, with the graphical library chosen, the task is to compare language
performance.

% About the real trending, ssg.

On the other hand, the real benchmark was performed on an existing application, the Sampling System GUI.
The ACS Sampling System is a collection of objects designed to easily sample an ACS Components Property
value over time~\cite{acssamp}.
The Sampling System GUI (SSG) is a client to the Sampling System written in Java, using the JChart2D library.
SSG communicates with several Sampling Managers to create Sampling Objects
and group them as needed, in order to sample properties, and finally plot the values
in user-time (i.e., as they arrive through the ACS Notification Channel~\cite{acs:notification_channel}).
SSG allows easy, quick visualization of system behavior during a period of time,
or under certain circumstances, and gives the possibility of visually correlating the values of
different properties of the system.

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "../article"
%%% End:
