%  article.tex (Version 3.3, released 19 January 2008)
%  Article to demonstrate format for SPIE Proceedings
%  Special instructions are included in this file after the
%  symbol %>>>>
%  Numerous commands are commented out, but included to show how
%  to effect various options, e.g., to print page numbers, etc.
%  This LaTeX source file is composed for LaTeX2e.

%  The following commands have been added in the SPIE class
%  file (spie.cls) and will not be understood in other classes:
%  \supit{}, \authorinfo{}, \skiplinehalf, \keywords{}
%  The bibliography style file is called spiebib.bst,
%  which replaces the standard style unstr.bst.

\documentclass[]{styles/spie}  %>>> use for US letter paper
%%\documentclass[a4paper]{spie}  %>>> use this instead for A4 paper
%%\documentclass[nocompress]{spie}  %>>> to avoid compression of citations
%% \addtolength{\voffset}{9mm}   %>>> moves text field down
%% \renewcommand{\baselinestretch}{1.65}   %>>> 1.65 for double spacing, 1.25 for 1.5 spacing
%  The following command loads a graphics package to include images
%  in the document. It may be necessary to specify a DVI driver option,
%  e.g., [dvips], but that may be inappropriate for some LaTeX
%  installations.
\usepackage[]{graphicx}
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage{subfigure}
\usepackage{amsmath}
%\usepackage[]{hyperref}
\title{High Performance Graphical Data Trending in a Distributed System}

%>>>> The author is responsible for formatting the
%  author list and their institutions.  Use  \skiplinehalf
%  to separate author list from addresses and between each address.
%  The correspondence between each author and his/her address
%  can be indicated with a superscript in italics,
%  which is easily obtained with \supit{}.

\author{Cristi\'an Maureira\supit{a},
        Arturo Hoffstadt\supit{a},
        Joao L\'opez\supit{a},
        Nicol\'as Troncoso\supit{b},
        Rodrigo Tobar\supit{c},
        Horst H. von Brand\supit{a}.
\skiplinehalf
\supit{a}Computer Systems Research Group,
          Universidad T\'ecnica Federico Santa Mar\'{\i}a,
          Valpara\'{\i}so, Chile; \\
\supit{b}Associated Universities, Inc. (AUI), Santiago, Chile;
         Universidad T\'ecnica Federico Santa Mar\'{\i}a,
         Valpara\'{i}so, Chile\\
\supit{c}European Southern Observatory,
         Garching bei München, Germany
}

%>>>> Further information about the authors, other than their
%  institution and addresses, should be included as a footnote,
%  which is facilitated by the \authorinfo{} command.

\authorinfo{Contact information: (Send correspondence to Cristi\'an Maureira) E-mail: cmaureir@csrg.inf.utfsm.cl, Telephone: +56 32 2654562, Web: \url{http://alma.inf.utfsm.cl}.}
%%>>>> when using amstex, you need to use @@ instead of @


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%>>>> uncomment following for page numbers
% \pagestyle{plain}
%>>>> uncomment following to start page numbering at 301
%\setcounter{page}{301}

  \begin{document}
  \maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
Trending near real-time data is a complex task, specially in distributed
environments. This problem was typically tackled in financial and transaction
systems, but it now applies to its utmost in other contexts, such as hardware
monitoring in large-scale projects. Data handling requires subscription to
specific data feeds that need to be implemented avoiding replication, and rate of transmission has to be assured. On the side of the graphical client,
rendering needs to be fast enough so it may be perceived as real-time processing
and display.

ALMA Common Software (ACS) provides a software
infrastructure for distributed projects which may require trending large
volumes of data. For theses requirements ACS offers a Sampling System, which
allows sampling selected data feeds at different frequencies. Along with this,
it provides a graphical tool to plot the collected information, which needs
to perform as well as possible.

Currently there are many graphical libraries available for data trending. This
imposes a problem when trying to choose one: It is necessary to know which has
the best performance, and which combination of programming language and library
is the best decision.
This document analyzes the performance of different graphical libraries and
languages in order to present the optimal environment when writing or
re-factoring an application using trending technologies in distributed systems.
To properly address the complexity of the problem, a specific set of alternative
was pre-selected, including libraries in Java and Python, languages which are
part of ACS. A stress benchmark will be developed in a simulated distributed
environment using ACS in order to test the trending libraries.
\end{abstract}

%>>>> Include a list of keywords after the abstract

\keywords{Trending, Plotting, Benchmarking, Distributed Systems, ACS}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Introduction}
\label{sec:intro}  % \label{} allows reference to this section
\input{src/introduction}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Problem}
\label{sec:problem}
\input{src/problem}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{State of art}
\label{sec:state}
\input{src/state}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Methodology Proposal}
\label{sec:method}
\input{src/method}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Graphical Library Benchmark}
\label{sec:gbenchmark}
\input{src/gbenchmark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Real Benchmark}
\label{sec:benchmark}
\input{src/benchmark}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusions}
\label{sec:conclusions}
\input{src/conclusions}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\appendix    %>>>> this command starts appendixes
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments     %>>>> equivalent to \section*{ACKNOWLEDGMENTS}

This work and the associated research has been conducted with funds granted by CONICYT, specifically ALMA-CONICYT grant \#31090034 and \#31080031.
Horst H. von Brand's work was also supported in part
by Centro Cient\'\i fico-Tecnol\'ogico de Valpara\'\i so (CCTVal) grant FB0821.
Without their help, this work would have been impossible.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%% References %%%%%
\hfill
\bibliography{report}   %>>>> bibliography data in report.bib
\bibliographystyle{styles/spiebib}   %>>>> makes bibtex use spiebib.bst

\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
